---
title: "Google Revenue"
output: html_notebook
---

# Notes

Pretty comprehensive R Tutorials List   
http://r-statistics.co/

# Libraries

```{r Libraries, eval=TRUE, message=TRUE, warning=FALSE}
library(data.table)
library(skimr)
library(highcharter)
library(plotly)
library(jsonlite)
library(dplyr)
library(tidyr)
library(tidyverse)
library(shiny)
library(ggplot2)
```

# Import Data

```{r Import eval=TRUE, message=FALSE, warning=FALSE}
filepath <- "/Users/zenolee/R/Kggl_Google_Revenue/Data"
df.train <- read_csv(paste(filepath, "train.csv",sep="/"), n_max=10000)
#df.train <- fread("G:/Zeno/Kaggle/kggl_Google_Revenue/Data/train.csv",stringsAsFactors = TRUE, nrows=10000)
```

```{r summary, eval=TRUE, message=FALSE}
summary(df.train)
```

# Uniqueness

```{r}
n_distinct(df.train$fullVisitorId)
n_distinct(df.train$sessionId)
n_distinct(df.train$visitId)

n_distinct(df.train$visitId,df.train$visitNumber)
```

There are a total of 903653 rows in the dataset, yet there doesn't appear to be a single field that is unique.  So, there are "dups" in the data

```{r Json_Conversion, eval=TRUE, message=FALSE, warning=FALSE}
tr_device <- paste("[", paste(df.train$device, collapse = ","), "]") %>% fromJSON(flatten = T)
tr_geoNetwork <- paste("[", paste(df.train$geoNetwork, collapse = ","), "]") %>% fromJSON(flatten = T)
tr_totals <- paste("[", paste(df.train$totals, collapse = ","), "]") %>% fromJSON(flatten = T)
tr_trafficSource <- paste("[", paste(df.train$trafficSource, collapse = ","), "]") %>% fromJSON(flatten = T)

```

## device

```{r}
tr_device %>% skim() %>% kable()
```

```{r}
str(tr_device)
```


```{r}
tr_geoNetwork %>% skim()
```

```{r}
tr_totals %>% skim()
```

```{r}
tr_trafficSource %>% skim()
```


# Data Quality Check Per Table

To make this process more efficient, I want to remove any columns that I don't believe will be necessary.  i.e. if 99% of the data is NULL or Unknown, it will not be significant for modeling.

```{r}

```



```{r}
df.train %>% select(-device,-geoNetwork, -totals,-trafficSource) %>% bind_cols(tr_device, tr_geoNetwork, tr_totals, tr_trafficSource)
```

# ggplot 

```{r}
ggplot(diamonds) + geom_point(aes(x=carat, y=price, color=cut)) + geom_smooth(aes(x=carat, y=price, color=cut))
```

